Reply To Examiners

### 2014-05-02 answer_thesis_examiner/chap1.tex
auto

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
\end{longtable}

\rowcolors{1}{white}{}
\replyToComment
    {Page 14: With reference to Equations 2.1, 2.2, 2.3 what are the range of $A_x$, $A$ and $I$}
    {The range of $A_x$ is from $(-\infty, \infty)$, and the range of both $A$ and $I$ is from $(0,\infty)$}

@@

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
15 & 6 & missing explaination for $E,B$ & explaination added \\
\end{longtable}

>>>>

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
\endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in numbers and independent in nature, \\
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
\end{longtable}    
\rowcolors{1}{white}{}

\replyToComment
    {Page 14: With reference to Equations 2.1, 2.2, 2.3 what are the range of $A_x$, $A$ and $I$}
    {The range of $A_x$ is from $(-\infty, \infty)$, and the range of both $A$ and $I$ is from $(0,\infty)$}

@@

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
15 & 6 & missing explaination for $\vec{E},B$ & explaination added \\
15 & 12 & x,y plane & x \& y planes \\
15 & -2 & $2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi)$ & $2 \frac{\xi_x(t) \xi_y(t)}{E_x^0 E_y^0} \cos (\Delta \phi)$ \\
16 & 2 & The parameters ... are: & The parameters ... are: the intensity orientation angle ($\theta$), the ellipticity angle ($\Psi$) and the orientation angle ($\chi$) \\
17 & 4 & machenics & mechanics \\
17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
\end{longtable}    
\rowcolors{1}{white}{}
